On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-04-01 docs/mvfits_paper/mvf.tex
Rm Schmidt et al. (2015) modeling citation [20]
Fix typos [11]

\cite{Hannam:2013oca, London:2017bcn, Khan:2015jqa, Schmidt:2014iyl, Mehta:2017jpq,Khan:2018fmp}.

@@

In section \sec{meth}, we outline the \gmvp{} and \gmvr{} algorithms.

@@

The refinement process is to terminate when a measure of model error (e.g. the $L^2$ norm $||\vec{g}^{(0)}-\vec{g}^{(n)}||$) passes a predetermined threshold. For \cite{lionel_london_2018_1402516} the following model representation error was used

@@

  \operatorname{Var}\left(\vec{a}\right)  = \frac{1}{J}\sum_{j=0}^{J}\left(d_j - \frac{1}{J}\sum_{u=0}^{J}d_u\right)^2

>>>>

\cite{Hannam:2013oca, London:2017bcn, Khan:2015jqa, Mehta:2017jpq,Khan:2018fmp}.

@@

In \sec{meth}, we outline the \gmvp{} and \gmvr{} algorithms.

@@

The refinement process is to terminate when a measure of model error (e.g. the $L^2$ norm $||\vec{g}^{(0)}-\vec{g}^{(n)}||$) passes a predetermined threshold. For the results presented in \sec{results} the following model representation error was used

@@

  \operatorname{Var}\left(\vec{d}\right)  = \frac{1}{J}\sum_{j=0}^{J}\left(d_j - \frac{1}{J}\sum_{u=0}^{J}d_u\right)^2
